---
title: "Data Visualization HW"
author: "Songwut Khongrung"
date: "2023-07-05"
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
---
## **5 Chart in every day used**
5 Chart in below i very proud to present .

### **1. Histogram**
  
  It simple chart . we have to use it and easily to understand
  
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(tidyverse)
ggplot(diamonds,
  mapping = aes(x=price))+
  geom_histogram(bins=50,color="#19A7CE",fill="#146C94",alpha=0.5)+
  theme_minimal()
#bins ความถี่ของข้อมูล
#color สีของเส้นกราฟ
#fill สีของกราฟ
#alpha ความคมชัด
```

This chart show frequency of data. In above chart is Positively Skewed.

### **2.density**

  It similar histogram but show line
```{r}
 ggplot(diamonds,
  mapping = aes(x=carat,))+
  geom_density(color="#19A7CE")+
  theme_minimal()
```
  
  This result seem histogram . most frequency have between 0-1 data make it Positively Skewed.
  
  If we use data not cleansing data. make it error result
  
### **3.Bar**

  This bar chart very popular .I think everyone know this chart

```{r}
ggplot(diamonds ,
  mapping = aes(x=cut))+
  geom_bar()+
  theme_minimal()
```

 quality of diamonds in data set we have quality ideal the most . 
 
 quality ideal many times more than quality fair
 
 I need to show other chart but it seem above chart
 
```{r}
 ggplot( diamonds,
  mapping = aes(x=cut,y=mean(price)))+
  geom_col(fill="#0E8388")+
  theme_minimal()+
  scale_y_continuous(labels = scales::comma)# Format y-axis labels with commas
```
 
  price average follow quality . High quality high price .low quality low price
  
```{r}
 ggplot(diamonds,
  mapping = aes(x=cut,fill=color))+
  geom_bar(position = "fill")+ #position have  fill  stack indensity   dodge
  theme_minimal()
```

  geom_bar in R can use function position for different output.
  
  this chart show volume percentage. we can see volume for quality by color
  

### **4.Box plot and violin plot**

  Box charts and violin charts. 
  
  very used in data job .
  
  We should to know and use it
  
```{r message=FALSE, warning=FALSE}
library(ggthemes)
library(patchwork)
P1<- ggplot(diamonds,
       aes(x=color,y=price)) +
  geom_boxplot(fill="#ABC270")+
  theme_wsj()

P2<- ggplot(diamonds,
            aes(x=color,y=price)) +
  geom_violin(fill="#ABC270")+
  theme_wsj()

P1+P2 # from library(patchwork) กราฟจะต่อกันถ้า + กัน สามารถเลื่อนลงมาข้างล่างได้ โดยเครื่องหมาย /
```

  boxplot we know about outlier. 
  
  we can see outlier but box plot can't see frequency.
  
  chart above so many outlier can cut outlier for quality data.
  
  violin can see  frequency but not show  outlier.
  
### **5.point**

  most very popular to use 
  
```{r}
ggplot(sample_frac(diamonds,0.08),
       aes(x=carat,y=price,col=cut))+
      geom_point()+
  theme_wsj()
```
  
  this chart show frequency between two columns.
  
  In data low price and low weight most frequency .
  
  but we can see quality by color
  
```{r}
ggplot(sample_frac(diamonds,0.08),
       aes(x=carat,y=price,col=cut))+
      geom_point()+
      geom_rug()+
  theme_minimal()
```
  
  can put more chart in chart . in chart above we see  frequency  very clery

